---
title: "Introduction to Git and GitHubr"
author: "Benjamin Soltoff"
date: "`r lubridate::today()`"
output: html_document
---

```{r setup, include=FALSE}
set.seed(123)
options(digits = 3)

knitr::opts_chunk$set(
  collapse = TRUE,
  cache = FALSE,
  message = FALSE,
  warning = FALSE,
  out.width = "80%",
  fig.align = "center",
  fig.width = 6,
  fig.asp = 0.618 # 1 / phi
)

library(tidyverse)
library(knitr)
library(here)
```

# What is Git? What is GitHub?

## Git


## GitHub


## Why should I use Git and GitHub?


# Setting up Git

## Install Git


## Configure Git

#### From R

```r
## install if needed (do this exactly once):
## install.packages("usethis")

library(usethis)
use_git_config(user.name = "Jane Doe", user.email = "jane@example.org")
```

```r
usethis::git_default_branch_configure()
```

#### From the shell

```bash
git config --global user.name 'Jane Doe'
git config --global user.email 'jane@example.com'

git config --global init.defaultBranch main
```

# Create a local Git repository

## Initialize a Git repo


## Make a commit


## View commit history


# Connect RStudio and GitHub

## Sign up for GitHub


## Create a Personal Access Token (PAT) on GitHub


## Store PAT


# Workflows


## New project, GitHub first


### Push to GitHub


## Existing project, GitHub first


## Existing project, GitHub last

# Merge conflicts


# Collaboration

## Branching


## Pull requests


## Forking


# Additional features of GitHub

## Issues


## Private repos


## Make a GitHub repo browsable



# Acknowledgments {.toc-ignore}

- 

# Session information {.toc-ignore}

```{r session-info, cache = FALSE}
sessioninfo::session_info()
```
